\huge Tor's Usability for Censorship Circumvention

### 2016-04-15 pets2017-paper/pets2017-paper.tex
last commit of today: rearrange results section and add TODOs in comments.

%basic statistics (BAD SO FAR)
Results from statistical analyses say: 
\begin{itemize} 
	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
	\item{{\bfseries impact of configuration version on success rate is not significant.}
	Mann-Whitney, W = 5.5, p-value = 0.8248}
	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
	Mann-Whitney, W = 991, p-value = 0.3197}
\end{itemize}

@@

% looking at all factors' impact on success rate
A logistic regression model showing effects of censorship environment, interface version,
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in a participant failing. Xlab participants were more likely to succeed. 
Participants with the old version of the interface were more likely to fail.

Coefficients:
             Estimate Std. Error z value Pr(>|z|)  
(Intercept)   19.4556  1684.3342   0.012   0.9908  
envE2        -17.3458  1684.3342  -0.010   0.9918  
envE3        -19.2652  1684.3341  -0.011   0.9909  
versionOLD    -0.7095     0.5793  -1.225   0.2206  
poolxlab       1.1218     0.5968   1.880   0.0601 .
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

% looking at all factors' impact on time to completion
A linear regression model showing effects of censorship environment, interface version, 
and recruitment pool on success finds that a difficult censorship environment is the most
significant factor in taking a long time to complete the task. Participants with the old version
of the interface and participants recruited from Xlab were likely to take longer.

Coefficients:
            Estimate Std. Error t value Pr(>|t|)    
(Intercept)   -42.79      86.70  -0.494  0.62280    
envE2         300.65      90.13   3.336  0.00124 ** 
envE3         923.66     100.94   9.150 1.68e-14 ***
versionOLD    104.78      78.70   1.331  0.18642    
poolxlab       92.41      78.88   1.172  0.24445    
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

>>>>

@@

%%% SUCCESS RATE 
% TODO: impact of env on success (chi squared?.. Serge might be wrong on this) 
% TODO: impact of version on success (chi squared?.. Serge might be wrong on this)

%%% RIGHT CLAMP TIME 
% done
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

%%% RIGHT CLAMP ACTIVE TIME 
% TODO:  time to success graph with right clamped ``active time''
% TODO:  impact of env on time to success 
% TODO: impact of version on time to success

% basic statistics (BAD, NEED CHI SQUARED NOT KRUSKAL AND EXCLUDED DNFs)
%Results from statistical analyses say: 
%\begin{itemize} 
%	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
%	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
%	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
%	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
%	\item{{\bfseries impact of configuration version on success rate is not significant.}
%	Mann-Whitney, W = 5.5, p-value = 0.8248}
%	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
%	Mann-Whitney, W = 991, p-value = 0.3197}
%\end{itemize}

% looking at all factors' impact on success rate (SUCCESS RATHER THAN SUCCESS RATE?)
%A logistic regression model showing effects of censorship environment, interface version,
%and recruitment pool on success finds that a difficult censorship environment is the most
%significant factor in a participant failing. Xlab participants were more likely to succeed. 
%Participants with the old version of the interface were more likely to fail. 
%
%Coefficients:
%             Estimate Std. Error z value Pr(>|z|)  
%(Intercept)   19.4556  1684.3342   0.012   0.9908  
%envE2        -17.3458  1684.3342  -0.010   0.9918  
%envE3        -19.2652  1684.3341  -0.011   0.9909  
%versionOLD    -0.7095     0.5793  -1.225   0.2206  
%poolxlab       1.1218     0.5968   1.880   0.0601 .
%---
%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

% looking at all factors' impact on time to completion (BAD, EXCLUDED DNFs)
%A linear regression model showing effects of censorship environment, interface version, 
%and recruitment pool on success finds that a difficult censorship environment is the most
%significant factor in taking a long time to complete the task. Participants with the old version
%of the interface and participants recruited from Xlab were likely to take longer. 
%
%Coefficients:
%            Estimate Std. Error t value Pr(>|t|)    
%(Intercept)   -42.79      86.70  -0.494  0.62280    
%envE2         300.65      90.13   3.336  0.00124 ** 
%envE3         923.66     100.94   9.150 1.68e-14 ***
%versionOLD    104.78      78.70   1.331  0.18642    
%poolxlab       92.41      78.88   1.172  0.24445    
%---
%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
